%-------------------------
% Resume in Latex
% Author: Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Rohan Sharma} \\ \vspace{1pt}
    \small 956-078-4409 $|$ \href{mailto:x@x.com}{\underline{irohansharma95@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/rohansharma95/}{\underline{linkedin.com/in/rohansharma95}} $|$
    \href{https://github.com/grep-rohan}{\underline{github.com/grep-rohan}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {BML Munjal University}{Gurgaon, HR}
      {Bachelor of Technology in Computer Science}{Sep 2014 -- Aug 2018}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer II}{Nov 2022 -- Present}
      {Statiq}{Gurgaon, HR}
      \resumeItemListStart
       \resumeItem{Engineered a robust backend infrastructure for the \emph{Charging Station Management System (CSMS)} that improved data retrieval speed by 40\%, enhancing the overall user experience for over 500 active users monthly.}
       \resumeItem{Designed and implemented a caching strategy using Redis that improved data retrieval times by 40\%, enhancing the overall performance of the \emph{CSMS} for user interactions.}
        \resumeItem{Contributed to building a \emph{Charger Logistics Management System}, enhancing real-time station tracking and installation processes for over 50 stations.}
        \resumeItem{Aligned frontend and backend development processes to create a unified user experience, ultimately enhancing workflow efficiency.}
        \resumeItem{Conducted a thorough analysis of existing database structures and implemented best practices for data management; established a comprehensive documentation framework for future reference, reducing onboarding time for new hires by 30%.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Software Engineer}{Aug 2020 -- Jul 2021}
      {Ivy}{Hyderabad, TS}
      \resumeItemListStart
        \resumeItem{Engineered robust backend systems for a \emph{Bingo} game using Python and MySQL, resulting in a seamless real-time gameplay experience via WebSocket that enhanced user engagement for over 5,000 active players weekly.}
        \resumeItem{Created tools for back-office operations, improving game monitoring and management efficiency.}
        \resumeItem{Focused on code quality through reviews and testing, enhancing system reliability.}
    \resumeItemListEnd

    \resumeSubheading
      {Software Developer}{Jun 2018 -- Jul 2020}
      {ZestIOT - IoT/AI powered aviation platform}{Hyderabad, TS}
      \resumeItemListStart
        \resumeItem{Worked on the backend for an airport turnaround SaaS platform, transforming IoT data into useful insights for users.}
        \resumeItem{Developed a real-time system to calculate Off-Block Time for planes, streamlining airport operations.}
        \resumeItem{Contributed to a computer vision project to analyze airport retail footfall, improving operational decision-making.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
        \resumeProjectHeading
        {\textbf{Timetable Management System} $|$ \emph{Node.js, Express.js, HTML/CSS}}{Sep 2017 -- Dec 2017}
        \resumeItemListStart
            \resumeItem{Created a system for scheduling and managing academic timetables.}
            \resumeItem{Designed an intuitive interface for easy creation and modification of timetables for institutions.}
            \resumeItem{Integrated database management for storing course schedules and room allocations.}
            \resumeItem{GitHub: \href{https://github.com/grep-rohan/Timetable-Management-System}{\underline{github.com/grep-rohan/Timetable-Management-System}}}
        \resumeItemListEnd
    
      \resumeProjectHeading
          {\textbf{Gender Recognition by Voice} $|$ \emph{Python, Scikit-Learn, R}}{Apr 2017 -- May 2017}
          \resumeItemListStart
            \resumeItem{Trained and tested multiple machine learning models to predict gender using voice samples.}
            \resumeItem{Achieved 97\% accuracy using a Multi-Layer Perceptron (MLP) and compared the performance of different models.}
            \resumeItem{Focused on optimizing model performance through feature extraction and preprocessing.}
            \resumeItem{GitHub: \href{https://github.com/grep-rohan/GenderRecognitionByVoice}{\underline{github.com/grep-rohan/GenderRecognitionByVoice}}}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Go, C/C++, Java, JavaScript, HTML/CSS} \\
     \textbf{Frameworks}{: FastAPI, Django, Flask, Node.js, Express.js } \\
     \textbf{Databases}{: MySQL, MongoDB, Redis, InfluxDB} \\
     \textbf{Middlewares}{: REST, AMQP, WebSocket, RPC} \\
     \textbf{Developer Tools}{: Git, Linux, AWS, CI/CD, VS Code}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
